Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
remvoing a comment

\textbf{Related work:}
Similar studies have shown the relationship between different\todo{which?
  Social, technical?  Both?} attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
  a habit of saying something like ``...performed a very relevant study where
  they...'' in describing previous work.  This is needlessly wordy.  You can
  write the exact same sentence, more or less (I changed ``determine'' to
  ``show'', ``find'' might also work) without that clause} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor towards acceptance of a pull 
\todo{I think you mean something like ``in predicting acceptance'', not
  ``towards''; do they argue causality?}
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects and how this attributes\todo{wrong word (as in, this is a noun as
  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

>>>>

\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} show that the social connection between the developer initiating a
pull request and the project integrators is a key factor towards acceptance of a pull 
\todo{I think you mean something like ``in predicting acceptance'', not
  ``towards''; do they argue causality?}
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects and how this attributes\todo{wrong word (as in, this is a noun as
  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.
